---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geopopr

<!-- badges: start -->

<!-- badges: end -->

The goal of geopopr is to ...

Ainda em construção ... :-(

## Installation

You can install the development version of geopopr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ghnaves/geopopr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(geopopr)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

```{r}
pop_pyr('BRA',2030)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

# Estrutura de dados

**GeoPackage**: dados geoespaciais

**SQLite**: metadados e tabelas relacionais

**Parquet:** dados tabulares de grandes dimensões

Arquivos binários grandes (geotiff, etc.) armazenados diretamente no sistema de arquivos, com os caminhos em banco de dados.

# Fonte dos dados

United Nations. (2024). World Population Prospects 2024. <https://population.un.org/wpp/>
